### 2024-11-09 conteudo/tool/architecture.tex
Reviewing tool proposal - part 3

The Setup step consists of the Function Breaker and the Code Duplication Finder. The pipeline of this step works as follows: the Function Parser receives the codebase the user is interested in, extracts the functions of the codebase along with metadata, and creates a new temporary codebase where the functions extracted become new code files. The Code Duplication Finder iterates over every pair of files in the temporary codebase, checks if they are code clones, and, if so, saves them in the Code Duplication Database, which is a text file that stores every code duplication as a triple \textbf{<function1,function2,similarity>}, where \textbf{function1} and \textbf{function2} are the functions that are duplicates of each other, and \textbf{similarity} is the metric given by the code duplication detection method utilized, which in our case is the cosine similarity explained in \ref{sec:similarity}. Finally, the Query Responder consumes the temporary codebase and the Code Duplication Database to extract duplicated functions-related information per user request. Figure \ref{fig:diagram} illustrates the tool pipeline. An explanation of how each component works is provided in this section.

>>>>

The Setup step consists of the Function Breaker and the Code Duplication Finder. The pipeline of this step works as follows: the Function Parser receives the codebase the user is interested in, extracts the functions of the codebase along with metadata, and creates a new temporary codebase where the functions extracted become new code files. The Code Duplication Finder iterates over every pair of files in the temporary codebase, checks if they are code clones, and, if so, saves them in the Code Duplication Database, which is a text file that stores every code duplication as a triple \textbf{<function1,function2,similarity>}, where \textbf{function1} and \textbf{function2} are the functions that are duplicates of each other, and \textbf{similarity} is the metric given by the code duplication detection method utilized, which in our case is the cosine similarity explained in Section \ref{sec:similarity}. Finally, the Query Responder consumes the temporary codebase and the Code Duplication Database to extract duplicated functions-related information per user request. Figure \ref{fig:diagram} illustrates the tool pipeline. An explanation of how each component works is provided in this section.
